Manuscript

### 2018-12-17 manuscript.Rmd
update Rmd

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset, variable) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  if(variable == "GE") {
    use_data <- filter(use_data, !is.na(RPKM))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
      return(pearson_res)
    }
  }
  else if(variable == "CN") {
    use_data <- filter(use_data, !is.na(CN))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
      return(pearson_res)
    }
  }
}
```

@@

g2p_druggenelins <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_drug_genes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# Filter drug screen datasets for G2P drug-gene-lineage associations
ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

@@

```{r}
crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                    summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Metric = "Gene Expression")

crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                    summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Metric = "Copy Number")

crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                    summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Metric = "Gene Expression")

crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                    summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
                              corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Metric = "Copy Number")
```

@@

```{r}
g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_p_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_p_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_p_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))

>>>>

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset, variable) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  if(variable == "GE") {
    use_data <- filter(use_data, !is.na(RPKM))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
      return(pearson_res)
    }
  }
  else if(variable == "CN") {
    use_data <- filter(use_data, !is.na(CN))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
      return(pearson_res)
    }
  }
}
```

@@

g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_druggenes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# Filter drug screen datasets for G2P drug-gene-lineage associations
ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

@@

```{r}
crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Gene Expression")
crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Copy Number")
crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Gene Expression")
crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Copy Number")
```

@@

```{r}
g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
